\chapter{Leveraging Social Context for Topic Evolution}
\label{kdd_chapter}
Topic discovery and evolution (TDE) has been a problem which has gained
long standing interest in the research community.  The goal in
topic discovery is to identify groups of keywords from large corpora so that the information in those
corpora are summarized succinctly.  The nature of text corpora has changed
dramatically in the past few years with the advent of social media.  
Social media services allow users to constantly share, follow and comment
on posts from other users.  Hence, such services have given a new
dimension to the traditional text corpus.  The new dimension being that
today's corpora have a \emph{social context} embedded in them in terms of the
community of users interested in a particular post, their profiles etc.  
We wish to harness this social context that comes along with
the textual content for TDE.  In particular, our goal is to both
qualitatively and quantitatively analyze when
social context actually helps with TDE.
Methodologically, we approach the problem of TDE by a proposing non-negative matrix
factorization (NMF) based model 
that incorporates both the textual information
and social context information.  We
perform experiments on large scale real world
dataset of news articles, and use Twitter as the platform providing information
about the social context of these news articles.
We compare with and outperform
several state-of-the-art baselines. Our conclusion is that using
the social context information is most useful when
faced with topics that are particularly difficult to detect.
\section{Introduction}
\label{sec:introduction}
\input{KDD/introduction.tex}

\section{Comparison to previous work}
\label{sec:comparison_to_previous_work}
\input{KDD/comparison_to_previous_work.tex}

\section{Learning from content and social media activity}
\label{sec:content_and_networks}
\input{KDD/content_and_networks.tex}

\section{DATA SET DESCRIPTION}
\label{sec:data_set_description}
\input{KDD/data_set_description.tex}

\section{Experiments}
\label{sec:experiments}
\input{KDD/experiments.tex}

\section{Conclusion}
\label{sec:conclusion}
The goal of our work was to gain a better understanding of when social context
helps in modeling topic evolution.  In order to achieve this, we proposed a matrix factorization based
approach which takes into account both the content of the documents and their social
context.  We found that, depending on the kind of topic, there is a clear trade
off between the content and community.
The content of the document
suffices if the text of the topic is very focused, and evolves little over time.
As we begin to move away from this scenario to consider documents that have a richer
and more variable vocabulary, we find that the use of social context
begins to help greatly.  We were also able to show
that our model can learn the kind of topics at hand; i.e., whether they are
content stable, community stable, or
both.

This work predominantly considered the user interactions of the documents
as the social context.  In the same spirit, one could explore what it means to consider
other types of contexts like geographical location of the user (or document),
and also perhaps delve more into the user profiles and incorporate information
about age, gender and demographics to give a well rounded view of the social context.
We hope to be able to work on these aspects in the future.
